
```{r}
#| echo: false
#| include: false
res_neg_aff_on_first_exam <-
  readRDS("./rds/res_neg_aff_on_first_exam.rds")
res_neg_aff_on_first_exam
```

```{r}
#| echo: false
#| include: false
res_neg_aff_on_second_exam <-
  readRDS("./rds/res_neg_aff_on_second_exam.rds")
res_neg_aff_on_second_exam
```

In an additional analysis, we investigated whether temporal segmentation—defined as assessments conducted immediately before an exam, immediately after an exam, and during periods unrelated to academic examinations—impacts levels of personal concern (*i.e.*, stress). To address this question, we compared the average levels of negative affect across these three time points. During the study period, students were subjected to two separate exams. The results revealed a consistent pattern across both examinations, with a marked reduction in negative affect from the day before to the day after the exams.

For the first exam, we observed a substantial standardized decrease in negative affect the day following the exam compared to the day prior. The decrease was -0.92 (Standard Error, $SE = 0.10$), corresponding to a Cohen's $d$ of -0.98, with an 89% CI of [-1.23, -0.78]. Similarly, for the second exam, the standardized decrease in negative affect was -0.39 ($SE = 0.08$), yielding a Cohen's $d$ of -0.54, with an 89% CI of [-0.75, -0.36].

